updated_workflow

### 2024-04-12 README.Rmd
fixed a bunch of stuff.
updated readme

The goal of msp-ms is provide a concise code-base for the normalization and data processing required for the msp-ms method.

Additionally, we provide a graphical user interface powered by shiny apps that allows for a user to utilize the method without requiring any R coding knowledge.

@@

## Combining Peaks file outputs

@@

```{r}
### Loading the files ###
lfq_filename = "legacy/protein-peptides-lfq.csv"
#file "protein-peptides.csv" exported from PEAKS identification
id_filename = "legacy/protein-peptides-id.csv"

@@

## Normalizing values.

@@

## Handling Outliers

Here we use a dixion test from the outliers package to detect outliers from each of our replicates.

@@

## Imputation of data

@@

## Joining with Library

@@

## Calcuating clevages
Next, we need to determine where the peptide sequences are cleaved.

@@

## Conducting stats

>>>>

The goal of mspms is provide a concise code-base for the normalization and data processing required to analyze data from the [Multiplex Substrate Profiling by Mass Spectrometry (MSP-MS) method](https://pubmed.ncbi.nlm.nih.gov/36948708/).

Additionally, we provide a [graphical user interface powered by shiny apps](https://gonzalezlab.shinyapps.io/mspms_shiny/) that allows for a user to utilize the method without requiring any R coding knowledge.

## Installation

You can install the released version of mspms from github

```{r,eval = FALSE}
devtools::install_github("baynec2/mspms")
```

## Workflow

@@

### Combining Peaks file outputs

@@

```{r}
library(dplyr)
library(mspms)

### Loading the files ###
lfq_filename = "legacy/protein-peptides-lfq.csv"
#file "protein-peptides.csv" exported from PEAKS identification
id_filename = "legacy/protein-peptides-id.csv"

@@

### Normalizing values.

@@

### Handling Outliers

Here we use a dixon test from the outliers package to detect outliers from each of our replicates.

@@

### Imputation of data

@@

### Joining with Library

@@

### Calcuating clevages
Next, we need to determine where the peptide sequences are cleaved.

@@

### Conducting stats
